Timeliness of security updates for Android

### 2014-08-13 securityupdates.tex
Fix width of figures to use columnwidth
Add full version graphs for best and worst models to show that they are reasonably classed as such
Add the start of a missing citation after I stumbled across it

\documentclass[conference,a4paper,twoside]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\graphicspath{figures/}
\usepackage{import}
\usepackage{url}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{tikz}
\RequirePackage[date=terse, isbn=true, doi=true, url=false, urldate=iso8601, maxbibnames=9, backref=false, backend=bibtex]{biblatex}
\addbibresource{securityupdates.bib}
\renewcommand{\bibfont}{\small}

@@

\begin{figure}
 \includegraphics[width=0.5\textwidth]{figures/nvulnerabilities_heat.pdf}
 \caption{Proportion of devices affected by different vulnerabilities}
 \label{fig:nvulnerabilities_heat}
\end{figure}

Those graphs summarise data across all the devices, however one of the advantages of the Device Analyzer data is that it allows us to look at what happens to individual devices over time.
Figure~\ref{fig:device_data} shows how the number of vulnerabilities affecting the \daNumDeviceDataDevices\ devices which have contributed the most days of data to Device Analyzer changes over time.
The trend that we saw in Figure~\ref{fig:proportioninsecure} of security improving and then getting worse is also shown here.
It shows how some devices had vulnerabilities, which were fixed, and then further vulnerabilities were discovered, and for these devices, mostly not fixed.
\begin{figure}
 \includegraphics[width=0.5\textwidth]{figures/device-data-all-security}
 \caption{Number of vulnerabilities affecting the top \daNumDeviceDataDevices\ devices by days of contribution in the Device Analyzer data}
 \label{fig:device_data}
\end{figure}

\subsection{Update frequency}
%TODO find out what the frequency of updates is
\begin{figure}
 \includegraphics[width=0.5\textwidth]{figures/from_to_updates.pdf}
 \caption{Updates between different Android versions in the DA data}
 \label{fig:from_to_updates}
\end{figure}
\begin{figure}
 \includegraphics[width=0.5\textwidth]{figures/w_security_updates.pdf}
 \caption{Number of updates each week which fixed or may have fixed security vulnerabilities}
 \label{fig:weekly_security_updates}
\end{figure}
Figure~\ref{fig:from_to_updates} shows how devices upgrade between different versions of Android.
Device Analyzer (DA) observes upgrade events and the figure shows which versions a device is upgrading from and to.
Mostly the dark cells are above the diagonal and are upgrades (\daNumUpdatesUpgrades).
While many upgrades are from one version to the next version there are also a fair number which skip a few versions.
Surprisingly there are also a small number of downgrade events (\daNumUpdatesDowngrades, \daPercUpdatesDowngrades) when older versions of Android are installed on to devices.
Possible reasons why users are downgrading are to free up space on their device, to make it easier to root or because a new version introduced bugs.

@@

\section{Discussion}
There are continuing efforts to reduce the impact of root vulnerabilities, both in Android and more widely.
SEAndroid~\cite{Smalley2013} which is included in Android from version XXX~\cite{TODO} claimed to prevent some root vulnerabilities and to reduce the impact of others.
Capability based enforcement systems such as Capsicum~\cite{Watson2010} substantially reduce the capabilities that an exploit has to try and gain increased privilege with.
When Capsicum is included in Linux~\cite{TODO} and hence in Android, it could be used to place fine grained restrictions on system daemons, preventing vulnerabilities becoming root vulnerabilities.

>>>>

\documentclass[conference,a4paper,twoside]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[space]{grffile}
\graphicspath{figures/}
\usepackage{import}
\usepackage{url}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{tikz}
\RequirePackage[date=terse, isbn=true, doi=true, url=false, urldate=iso8601, maxbibnames=9, backref=false, backend=bibtex]{biblatex}
\addbibresource{securityupdates.bib}
\renewcommand{\bibfont}{\small}

@@

\begin{figure}
 \includegraphics[width=\columnwidth]{figures/nvulnerabilities_heat.pdf}
 \caption{Proportion of devices affected by different vulnerabilities}
 \label{fig:nvulnerabilities_heat}
\end{figure}

Those graphs summarise data across all the devices, however one of the advantages of the Device Analyzer data is that it allows us to look at what happens to individual devices over time.
Figure~\ref{fig:device_data} shows how the number of vulnerabilities affecting the \daNumDeviceDataDevices\ devices which have contributed the most days of data to Device Analyzer changes over time.
The trend that we saw in Figure~\ref{fig:proportioninsecure} of security improving and then getting worse is also shown here.
It shows how some devices had vulnerabilities, which were fixed, and then further vulnerabilities were discovered, and for these devices, mostly not fixed.
\begin{figure}
 \includegraphics[width=\columnwidth]{figures/device-data-all-security}
 \caption{Number of vulnerabilities affecting the top \daNumDeviceDataDevices\ devices by days of contribution in the Device Analyzer data}
 \label{fig:device_data}
\end{figure}

\subsection{Update frequency}
%TODO find out what the frequency of updates is
\begin{figure}
 \includegraphics[width=\columnwidth]{figures/from_to_updates.pdf}
 \caption{Updates between different Android versions in the DA data}
 \label{fig:from_to_updates}
\end{figure}
\begin{figure}
 \includegraphics[width=\columnwidth]{figures/w_security_updates.pdf}
 \caption{Number of updates each week which fixed or may have fixed security vulnerabilities}
 \label{fig:weekly_security_updates}
\end{figure}
Figure~\ref{fig:from_to_updates} shows how devices upgrade between different versions of Android.
Device Analyzer (DA) observes upgrade events and the figure shows which versions a device is upgrading from and to.
Mostly the dark cells are above the diagonal and are upgrades (\daNumUpdatesUpgrades).
While many upgrades are from one version to the next version there are also a fair number which skip a few versions.
Surprisingly there are also a small number of downgrade events (\daNumUpdatesDowngrades, \daPercUpdatesDowngrades) when older versions of Android are installed on to devices.
Possible reasons why users are downgrading are to free up space on their device, to make it easier to root or because a new version introduced bugs.

@@

\section{Discussion}
There are continuing efforts to reduce the impact of root vulnerabilities, both in Android and more widely.
SEAndroid~\cite{Smalley2013} which is included in Android from version 4.1~\cite{https://developer.android.com/about/versions/jelly-bean.html} claimed to prevent some root vulnerabilities and to reduce the impact of others.
Capability based enforcement systems such as Capsicum~\cite{Watson2010} substantially reduce the capabilities that an exploit has to try and gain increased privilege with.
When Capsicum is included in Linux~\cite{TODO} and hence in Android, it could be used to place fine grained restrictions on system daemons, preventing vulnerabilities becoming root vulnerabilities.
